Multi-line Intensity Mapping

### 2019-04-15 paper/ms.tex
Make thoughts section more clear
Add caption to both figs

\begin{figure}[h!]
\begin{center}
\includegraphics{fig/corner_Nconstant.pdf}
\end{center}
\caption{Caption.}
\label{fig:tf_Nconst}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
\end{center}
\caption{Caption.}
\label{fig:tf_Nconst_Bhigher}
\end{figure}

As an illustration, we construct a corner plot in Figure~\ref{fig:tf_Nconst}
for the inferred bias values using toy values of $B_1^2 = 1$, $B_2^2 = 2$, and
$B_3^2 = 3$ along with $N_1, N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. The
units here are arbitrary. Since each line has the same value of $N$, the \SN{}
of each line is driven by the value of $B_i$, with $B_3$ having the highest
intrinsic \SN{} and $B_1$ the lowest. We make the same assumptions that go
into Equation~\ref{eq:fmat_tf_exp}, i.e. that we are white-noise dominated in
each line.B y plotting each axis as a fraction of the true value for each of
$B_1$, $B_2$, and $B_3$, we see that the marginalized posterior on each bias
factor is the same (\textit{diagonal panels}). This is equivalent to saying
that the fractional error on each bias factor is the same for each line.

@@

\section{Thoughts}
Like doing a matched filter??? Trying to understand intuitively why this
works. If you have a super well measured field, then its like you're God who
knows that the density field is. Its almost like using that density field as a
matched filter?

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics{fig/corner_Nconstant.pdf}
\end{center}
\caption{A toy corner plot showing the degeneracies between different lines
with different intrinsic \SN{} ratios under the white-noise dominated
assumption. We set $B_1^2 = 1$, $B_2^2 = 2$, and $B_3^2 = 3$ along with $N_1,
N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. Since each line has the same value
of $N$, the \SN{} of each line is driven by the value of $B_i$, with $B_3$
having the highest intrinsic \SN{} and $B_1$ the lowest. We plot each axis as
a fraction of the true value for each of $B_1$, $B_2$, and $B_3$, and see that
the marginalized posterior on each bias factor is the same (\textit{diagonal
panels}) as we expect from Equation~\ref{eq:frac_error_same}. There is a
strong negative covariance between $B_2$ and $B_3$, a mildly negative
covariance between $B_3$ and $B_1$, and a mildly positive covariance between
$B_1$ and $B_2$. An explanation for this behavior is given in the text.}
\label{fig:tf_Nconst}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
\end{center}
\caption{We perform the same procedure as in Figure~\ref{fig:tf_Nconst}, except
now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
$B_2^2 = 4$ and $B_3^2 = 9$. The values for each $N_i$ and $V_k$ are the same
as in Figure~\ref{fig:tf_Nconst}. We see that even though nothing about line
$1$ has changed (i.e. no additional measurements of line $1$ have been made),
the \SN{} on $B_1$ has improved because the fractional error on each line must
be the same (Equation~\ref{eq:frac_error_same}). The degeneracies between the
different lines discussed in Figure~\ref{fig:tf_Nconst} become stronger in
this case.}
\label{fig:tf_Nconst_Bhigher}
\end{figure}

As an illustration, we construct a corner plot in Figure~\ref{fig:tf_Nconst}
for the inferred bias values using toy values of $B_1^2 = 1$, $B_2^2 = 2$, and
$B_3^2 = 3$ along with $N_1, N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. The
units here are arbitrary. Since each line has the same value of $N$, the \SN{}
of each line is driven by the value of $B_i$, with $B_3$ having the highest
intrinsic \SN{} and $B_1$ the lowest. We make the same assumptions that go
into Equation~\ref{eq:fmat_tf_exp}, i.e. that we are white-noise dominated in
each line. By plotting each axis as a fraction of the true value for each of
$B_1$, $B_2$, and $B_3$, we see that the marginalized posterior on each bias
factor is the same (\textit{diagonal panels}). This is equivalent to saying
that the fractional error on each bias factor is the same for each line.

@@

\section{Random Thoughts}
Like doing a matched filter??? Trying to understand intuitively why this
works. If you have a super well measured field, then its like you're God who
knows that the density field is. Its almost like using that density field as a
matched filter?
